Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-12-05 Arxiv/main.tex
update accuracy analysis

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
If $Y \thicksim Lap(b)$, we have\cite{dwork2014algorithmic}:
$$
Pr[|Y| \geq t \cdot b] = e^{- t}.
$$
Based on this, we get:
\begin{equation*}
Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}
\end{equation*}
in our case, where $Y \thicksim Lap(\frac{\Delta \bysinfer}{\epsilon})$.

After post-processing (i.e., taking the floor value of $Y$), we get:
\[
Pr\big[\lfloor Y \rfloor = t\big] 
= Pr[ t \leq Y < t + 1] 
= \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
\]
when $t \geq 0$, and\\
\[
Pr\big[\lfloor Y \rfloor = t\big] 
= Pr[ t \leq Y < t + 1] 
= \frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
\]
when $t < 0$.\\

@@

\begin{itemize}
  \item[\textbf{t = 0}] $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.
  \item[\textbf{t = 1}]
  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$. 
  \item[\textbf{t = 2}]$\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.
\end{itemize}
In all cases above, probabilities are fixed whenever data size changes.

@@

@@

For comparison with Laplace mechanism, we developed the Table \ref{tab_acc_theo}.

\begin{table}[h!]
\scriptsize
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 c & 0 
 & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
  & $1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$  \\
 \hline
 $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
 & 0.19673467014 & 0.11932560927 & 0.07237464051 \\
 \hline
 $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & 0.31606027941 & 0.11627207896 & 0.04277410743 \\
 \hline
 $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & $\frac{1}{\nomalizer{\dataobs}}$ & $\frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ & \\
 \hline
\end{tabular}
\caption{Accuracy Comparison in Theoretical}
\label{tab_acc_theo}
\end{table}

In the case when $\alpha = \beta$, there are always 2 symmetric beta distributions with the same distance from the true posterior, then we have accuracy table as:
\begin{table}[h!]
\scriptsize
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 c & 0 
 & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
  & $1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$  \\
 \hline
 $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
 & 0.19673467014 & 0.31606027941 & 0.19170024978 \\
 \hline
 $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & 0.31606027941 & 0.43233235838 & 0.1590461864 \\
 \hline
 $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & $\frac{2}{\nomalizer{\dataobs}}$ & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ & \\
 \hline
\end{tabular}
\caption{Accuracy Comparison in Theoretical}
\label{tab_acc_theo}
\end{table}

The probability of getting the true posterior, or posterior with certain step from Laplace mechanism is fixed whatever the data size or prior changes.

>>>>

\subsubsection{Accuracy Bound for Laplace Mechanism}
\label{subsec_accuracy_lap}
Given $Y \thicksim \lap{0}{b}$, we have\cite{dwork2014algorithmic}:$Pr[|Y| \geq t \cdot b] = e^{- t}.$\\
Based on this, we get:$Pr[|Y| \geq t] = e^{- \frac{t \epsilon}{\Delta \bysinfer}}$, where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in our setting.\\

Considering the post-processing (i.e., taking the floor value of $Y$) in $\lapmech$, we have:
\[
Pr\big[\lfloor Y \rfloor = t\big] 
= Pr[ t \leq Y < t + 1] 
= \frac{1}{2} (e^{- \frac{\epsilon (t)}{\Delta \bysinfer}} - e^{- \frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
\]
when $t \geq 0$, and\\
\[
Pr\big[\lfloor Y \rfloor = t\big] 
= Pr[ t \leq Y < t + 1] 
= \frac{1}{2} (e^{\frac{\epsilon (t)}{\Delta \bysinfer}} - e^{\frac{\epsilon (t + 1)}{\Delta \bysinfer}}).
\]
when $t < 0$.

@@

Given $t$ with specific values ($1, 2, 3$ for example), we get following accuracy equations:

\begin{itemize}
  \item[\textbf{t = 0}] $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.19673467014$.
  \item[\textbf{t = 1}]
  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11932560927$. 
  \item[\textbf{t = 2}]$\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.07237464051$.
\end{itemize}
In all cases above, probability values are fixed even data size changes, only the distance are decreasing.

@@

Given $t$ with the same specific values ($1, 2, 3$ as above), we get following accuracy equations:

\begin{itemize}
  \item[\textbf{t = 0}] $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L ) = 0} = 0.31606027941$.
  \item[\textbf{t = 1}]
  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)} } = 0.11627207896$. 
  \item[\textbf{t = 2}]$\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), r_L )^2 = 1 - 
  \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
  \cdot
  \sqrt{1 - \frac{\frac{t}{2}}{\beta}}} = 0.04277410743$.
\end{itemize}
In all cases above, probability values are fixed even data size changes, only the distance are decreasing.

@@

\subsection{Accuracy Comparison between $\hexpmech$, $\lapmech$ and $\ilapmech$}
For comparison with Laplace mechanism, we developed the Table \ref{tab_acc_theo}.
\begin{table}[h!]
\scriptsize
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 c & 0 
 & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
    \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
 & $1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$  \\
 \hline
 $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
 & 0.19673467014 & 0.11932560927 & 0.07237464051 \\
 \hline
 $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & 0.31606027941 & 0.11627207896 & 0.04277410743 \\
 \hline
 $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & $\frac{1}{\nomalizer{\dataobs}}$
 & $\frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
 \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$
 & $\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}$\\
 \hline
\end{tabular}
\caption{Accuracy Comparison in Theoretical}
\label{tab_acc_theo}
\end{table}

In the case when $\alpha = \beta$, there are always 2 symmetric beta distributions with the same distance from the true posterior, then we have accuracy table as:
\begin{table}[h!]
\scriptsize
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 c & 0 
 & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
  & $1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$  \\
 \hline
 $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
 & 0.19673467014 & 0.31606027941 & 0.19170024978 \\
 \hline
 $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & 0.31606027941 & 0.43233235838 & 0.1590461864 \\
 \hline
 $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & $\frac{1}{\nomalizer{\dataobs}}$ & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ 
  &$\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}$\\
 \hline
\end{tabular}
\caption{Accuracy Comparison in Theoretical}
\label{tab_acc_theo}
\end{table}

When $\epsilon$ and dimensions are fixed, the probability of getting the true posterior, or posterior with certain step from Laplace mechanism is fixed whatever the data size or prior changes.

By solving following equations:
\begin{itemize}
  \item
\[
\frac{1}{\nomalizer{\dataobs}} = 0.19673467014
\]
we can get the range where we can do better than $\lapmech$ on outputting the correct answer and

\[
\frac{1}{\nomalizer{\dataobs}} = 0.31606027941
\]
we can get the range where we can do better than $\ilapmech$ on outputting the correct answer and

  \item 
  \item 
  \item 
  \item 
\end{itemize}
